Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2017-11-01 aggregation/agg-disclosure.tex
private aggregation

\subsection{Disclosure of Study Design}

@@

A disclosure containing these six elements satisfies most of the requirements established at the top of this section (the exception is ensuring the privacy of confidential data, which is treated later in the article):
\begin{itemize}
  \item The result is \textbf{computable} using Eq.~\ref{eqn:study};
  \item the computation is \textbf{complete} and \textbf{minimal} because all components are required and no superfluous components are included;
  \item The results are \textbf{reproducible} if the reader is able to accurately interpret the author's references in \ref{itm:bg} and \ref{itm:em};
  \item The disclosure includes only information for which the author can claim \textbf{authority};
  \item The disclosure includes only information for which the study is the \textbf{primary} source.
\end{itemize}
As mentioned, the proper interpretation of the disclosure requires that the reader accurately interprets the author's references to background databases and elementary flows, including mutually consistent implementation of the LCIA vector $\mathbf{e}$.  These aspects are out of scope for the purposes of this paper, and we will assume that a shared understanding between author and reader can be reached.  However, the the challenges of operationalizing this requirement are tremendously complex.  Some implications of the requirement for shared agreement are considered in the Discussion.

>>>>

\subsection{Contents of a Disclosure}

@@

A disclosure containing these six elements satisfies most of the requirements established at the top of this section (the exception is ensuring the privacy of confidential data, which is treated later in the article):
\begin{itemize}
  \item The result is \textbf{computable} using Eq.~\ref{eqn:study};
  \item the computation is \textbf{complete} and \textbf{minimal} because all components are required and no superfluous components are included;
  \item The results are \textbf{reproducible} if the reader is able to accurately interpret the author's references in \ref{itm:bg} and \ref{itm:em};
  \item The disclosure includes only information for which the author can claim \textbf{authority};
  \item The disclosure includes only information for which the study is the \textbf{primary} source.
\end{itemize}
As mentioned, the proper interpretation of the disclosure requires that the reader accurately interprets the author's references to background databases and elementary flows, including mutually consistent implementation of the LCIA vector $\mathbf{e}$.  These aspects are out of scope for the purposes of this paper, and we will assume that a shared understanding between author and reader can be reached.  However, the the challenges of operationalizing this requirement are complex.  Some implications on the information required for a successful disclosure are considered in the Discussion.

### 2017-11-01 aggregation/agg-objective.tex

In the context of this paper, an ``LCA Study'' should be understood as any aggregation of data under consideration, from a single-operation unit process to a full ISO-style product LCA.  The practice of reporting the results of an LCA study implies the existence of two parties with different information: the study author has full knowledge of the product system model; and the Reader only has knowledge of what the author has disclosed.  Obviously, the level of detail of the disclosure will determine how useful it is to the Reader.  In this context, the reader will want to know the answers to various review objectives.  
At the same time the author may have constraints that limit what she can disclose.  The purpose of the framework is to give form to the disclosure so that the requirements of various review objectives, and restrictions associated with various disclosure contraints, can be evaluated clearly.

@@

On the basis of transparency, the framework should meet the following objectives:
\begin{itemize}
\item \textbf{Computability}. The result should be computed using only the disclosure, plus resources available independently to the Reader.  The computation should follow the consensus understanding of process LCA computation.
\item \textbf{Completeness / Minimality}.  The computation should use all of the information provided in the disclosure.
\item \textbf{Reproducibility}.  The result obtained by the Reader should match the result provided by the Author.
\end{itemize}
One key objective of disclosure is to inspect the work of the Author.  Consequently, the disclosure should be made up of the Author's own work product and should exclude, for instance, data that were drawn from a reference database or other independent source and used in an unmodified form.  The purpose of this is twofold: to focus the efforts of the Reader on the work of the Author, and to enable the Reader to obtain and inspect the third-party data independently, thus ensuring its integrity.
\begin{itemize}
\item \textbf{Authority}.  The disclosure should include only information for which the Author is responsible.
\item \textbf{Primacy}.  The disclosure should exclude information that is made available by a third party.
\end{itemize}
In addition, because of the ubiquity of confidential and sensitive information in LCA, any operational disclosure framework must also meet the following:
\begin{itemize}
\item \textbf{Privacy}.  The disclosure should protect information that is held in confidence by the Author.
\end{itemize}

>>>>

In the context of this paper, an ``LCA Study'' should be understood as any aggregation of data under consideration, from a single-operation unit process to a full ISO-style product LCA.  The practice of reporting the results of an LCA study implies the existence of two parties with different information: the study author has full knowledge of the product system model; and the reader only has knowledge of what the author has disclosed.  Obviously, the level of detail of the disclosure will determine how useful it is to the reader.  In this context, the reader will want to know the answers to various review objectives.  
At the same time the author may have constraints that limit what she can disclose.  The purpose of the framework is to give form to the disclosure so that the requirements of various review objectives, and restrictions associated with various disclosure contraints, can be evaluated clearly.

@@

On the basis of transparency, the framework should meet the following objectives:
\begin{itemize}
\item \textbf{Computability}. The result should be computed using only the disclosure, plus resources available independently to the reader.  The computation should follow the consensus understanding of process LCA computation.
\item \textbf{Completeness / Minimality}.  The computation should use all of the information provided in the disclosure.
\item \textbf{Reproducibility}.  The result obtained by the reader should match the result provided by the author.
\end{itemize}
One key objective of disclosure is to inspect the work of the author.  Consequently, the disclosure should be made up of the author's own work product and should exclude, for instance, data that were drawn from a reference database or other independent source and used in an unmodified form.  The purpose of this is twofold: to focus the efforts of the reader on the work of the author, and to enable the reader to obtain and inspect the third-party data independently, thus ensuring its integrity.
\begin{itemize}
\item \textbf{Authority}.  The disclosure should include only information for which the author is responsible.
\item \textbf{Primacy}.  The disclosure should exclude information that is made available by a third party.
\end{itemize}
In addition, because of the ubiquity of confidential and sensitive information in LCA, any operational disclosure framework must also meet the following:
\begin{itemize}
\item \textbf{Privacy}.  The disclosure should protect information that is held in confidence by the author.
\end{itemize}

### 2017-11-01 aggregation/agg-review.tex

In current practice, this model is then documented as a written report, and the report can be both critically reviewed and distributed to data users, but this process introduces significant interpretive challenges.  It also results in the model being frozen to a particular configuration or set of configurations from which the results are generated.

>>>>

In current practice, this model is then documented as a written report, and the report can be both critically reviewed and distributed to data users, but this process introduces significant interpretive challenges.  It also results in the model being frozen to a particular configuration or set of configurations at the time the results are generated.  If the review objectives include sensitivity of the model to parameter variations and/or alternative scenarios, then the review is limited to only the parameters and scenarios considered by the author.
